ResultsNPS

### 2019-10-14 R/nps_reports/results.Rmd
changes in python to get additional data from batch to compare. and some changes in R.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source('functions/graphs_NPS.R')
source('functions/datasets_NPS.R')
quant_max <- 0.95
size <- params$size

@@

```{r infeasible_list}
infeasible_instances <- get_infeasible_instances(df)
infeasible_stats <- get_infeasible_stats(df)
```

@@

```{r infeasible}
infeasible_stats %>% kable
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source('functions.R')
source('datasets.R')
quant_max <- 0.95
size <- params$size

@@

```{r infeasible_list}
infeasible_instances <- get_infeasible_instances(df)
infeasible_stats <- get_infeasible_stats(df)
infeasible_times <- get_infeasible_times(df)
```

@@

```{r infeasible_stats}
infeasible_stats %>% kable
```

In addition, the times to detect the infeaseability of a given instance have been greatly reduced (to half, approximately) as can be see in the following table:

```{r infeasible_times}
infeasible_times %>% kable
```

@@

### Reducing variance

The variance in the frequency of maintenances is a side objective that was not been taken into account previously. To calculate it, we have, for each fleet type, measured the variance of the distance between maintenances. And we have summed all variances for all fleet types. We do this analysis for all integer solutions obtained.
As can be seen, in almost all of the cases there is a reduction in the variance. The mean relative difference is `r mean_var_reduction` and 95\% of instances have less than `r quant95_var_reduction`.

```{r variances}
variances <- get_variances(df)
var_per <- variances$dif_perc
mean_var_reduction <- var_per %>% mean
quant95_var_reduction <- var_per %>% quantile(quant_max)
qplot(var_per, xlab='Relative difference in variance (in % of base case) among integer solutions.')
```
